NFC and burnout in teachers - A replication and extension study

### 2022-07-20 Manuscript/Manuscript.Rmd
Update Manuscript.Rmd

Furthermore, we extended the analysis to other possible mediators.
These mediators were motivated by our own recent survey of the literature on NFC and well-being, which suggested that individuals high in NFC might not only have a high level of personal resources but also overestimate their own resources to a certain degree [@Zerna2021].
This can take the form of patients with higher NFC having lower intentions to consult their physician [@Latimer2007] or adults with higher NFC having higher intentions to consume high calorie beverages [@Gallivan2020] after detailed message interventions designed to promote consultations and healthier beverage choices, respectively.
Only a balance of resources and demands results in personal well-being, while an imbalance threatens well-being, regardless of whether this imbalance is in favour of resources or demands [@Dodge2012].
Following the framework of Hobfoll [-@Hobfoll1989], resources can be objects with practical or status purpose, conditions like marriage or tenure, personality aspects like coping style, and energies such as time, money, or knowledge.
In the case of NFC, resources are from the categories personality and energies: Personality, because NFC is a trait, encompassing a curious, analytic, and passionate approach to challenges, and energies, because individuals high in NFC have been coping actively all their life, which enriches their level of experience and knowledge in approaching challenges [@Cacioppo1996].
These personal resources matter with regard to stress assessment (how the situation is appraised) and with regard to both coping and recovery [@Salanova2006].
We therefore investigated whether the association of NFC and burnout was mediated by different ratios of demands and resources; demands that are too high to be dealt with using one’s personal resources (*demands too high*), demands that are too low for one’s personal resources (*demands too low*), and a balanced fit of demands and resources (*demand-resource-fit*).
Using the same data as for the replication, we computed a structural equation model (SEM) to assess the influence of these mediators.
Since individuals high in NFC are confident in their abilities [@Bye2009; @Ghorbani2004; @Heppner1983; @Klaczynski1996], we expected NFC to be negatively associated with *demands too high*, and positively associated with *demands too low* and *demand-resource-fit*.
And since burnout results from constant unpleasant activation by high demands, we expected it to be positively associated with *demands too high* and negatively associated with *demand-resource-fit*.
However, we had no hypothesis regarding the association of *demands too low* and burnout, because even though *demands too low* is akin to the concept of boredom and the consequences of boredom and burnout are very similar, burnout is a state with even lower activation and even more negative affect than boredom [@Schaufeli2014].
It has already been shown that the Covid-19 pandemic has exacerbated the rising prevalence of burnout [@Froebe2021], so we incorporated the degree of feeling burdened by the pandemic in an exploratory approach.
To sum up, this study had three aims: Replicating findings of mediation between NFC and burnout, investigating the impact of different demand-resource-ratios on the relationship between NFC and burnout, and exploring the impact of other variables such as perceived burden by the pandemic.

>>>>

Furthermore, we extended the analysis to other possible mediators.
These mediators were motivated by our own recent survey of the literature on NFC and well-being, which suggested that individuals high in NFC might not only have a high level of personal resources but also overestimate their own resources to a certain degree [@Zerna2021].
This can take the form of patients with higher NFC having lower intentions to consult their physician [@Latimer2007] or adults with higher NFC having higher intentions to consume high calorie beverages [@Gallivan2020] after detailed message interventions designed to promote consultations and healthier beverage choices, respectively.
Only a balance of resources and demands results in personal well-being, while an imbalance threatens well-being, regardless of whether this imbalance is in favour of resources or demands [@Dodge2012].
Following the framework of Hobfoll [-@Hobfoll1989], resources can be objects with practical or status purpose, conditions like marriage or tenure, personality aspects like coping style, and energies such as time, money, or knowledge.
In the case of NFC, resources are from the categories personality and energies: Personality, because NFC is a trait, encompassing a curious, analytic, and passionate approach to challenges, and energies, because individuals high in NFC have been coping actively all their life, which enriches their level of experience and knowledge in approaching challenges [@Cacioppo1996].
These personal resources matter with regard to stress assessment (how the situation is appraised) and with regard to both coping and recovery [@Salanova2006].
We therefore investigated whether the association of NFC and burnout was mediated by different ratios of demands and resources; demands that are too high to be dealt with using one’s personal resources (*demands too high*), demands that are too low for one’s personal resources (*demands too low*), and a balanced fit of demands and resources (*demand-resource-fit*).
Using the same data as for the replication, we computed a structural equation model (SEM) to assess the influence of these mediators.
Since individuals high in NFC are confident in their abilities [@Bye2009; @Ghorbani2004; @Heppner1983; @Klaczynski1996], we expected NFC to be negatively associated with *demands too high*, and positively associated with *demands too low* and *demand-resource-fit*.
And since burnout results from constant unpleasant activation by high demands, we expected it to be positively associated with *demands too high* and negatively associated with *demand-resource-fit*.
However, we had no hypothesis regarding the association of *demands too low* and burnout, because even though *demands too low* is akin to the concept of boredom and the consequences of boredom and burnout are very similar, burnout is a state with even lower activation and even more negative affect than boredom [@Schaufeli2014].
It has already been shown that the Covid-19 pandemic has exacerbated the rising prevalence of burnout [@Froebe2021], so we incorporated the degree of feeling burdened by the pandemic in an exploratory approach.
To sum up, this study had three aims: Replicating findings of mediation between NFC and burnout, investigating the impact of different demand-resource-ratios on the relationship between NFC and burnout, and exploring the impact of other variables such as perceived burden by the Covid-19 pandemic.
